---
title: "Ioslides template"
author: "Giuseppe Ragusa"
date: "1 Oct 2014"
output:  
  ioslides_presentation:    
    fig_caption: yes
    fig_height: 3.6
    fig_width: 5.5
    self_contained: no
    logo: logo.png
    css: myfonts.css
    
---

## R Markdown {.build}

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.cap="Fig 1. - Prova", fig.align='center'}
library(ggthemes)
library(AER)
library(grid)
data(CPSSW04)
ggplot(CPSSW04, aes(y=earnings, x = degree)) + stat_summary(fun.data = "mean_cl_boot", colour = "red") + grthemes:::theme_gr() + facet_grid(gender~age) + geom_smooth(aes(group=1), method="lm", sd=FALSE)
```

## Slide with Bullets

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

- Bullet 1
- Bullet 2
- Bullet 3

$$
f(x) := \int g(y,x) f(y) dy
$$

> - As you can seem this is very interesting!

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## Code highlight

```{r, echo=TRUE, tidy=FALSE}
r  <- rnorm(100)

x <- 10
y <- x * 2


```

## Two columns

```{r, fig.height=3, fig.align='center'}
ggplot(subset(CPSSW04, age<28), aes(y=earnings, x = degree)) + 
  stat_summary(fun.data = "mean_cl_boot", colour = "red") + 
  grthemes:::theme_gr() + facet_grid(gender~age) + 
  geom_smooth(aes(group=1), method="lm", sd=FALSE)
```

<div class="columns-2">
  

  - Bullet 1
  - Bullet 2
  - Bullet 3
</div>
